% LaTeX resume using res.cls
\documentclass[line,margin,11pt]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\addtolength{\oddsidemargin}{-.5in}
	\addtolength{\evensidemargin}{-.5in}
	\addtolength{\textwidth}{.6in}

	\addtolength{\topmargin}{-.5in}
	\addtolength{\textheight}{1.75in}
\begin{document}

\name{Kyle Wenholz}
% \address used twice to have two lines of address
\address{1311 N. Alder, Tacoma, WA 98406}
\address{(406) 546-9210, kwenholz@pugetsound.edu}

 
\begin{resume}
\vspace*{.15cm}
\section{OBJECTIVE} Mathematics and English Tutoring Position 
 
\section{EDUCATION} {\sl Bachelor of Science} \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                University of Puget Sound, Tacoma, WA 
                expected June 2013 \\
                Majors: Mathematics, Computer Science \\
                Cumulative GPA: 3.77

\vspace*{.1cm}

 
\section{EXPERIENCE} 
{\sl Computer Science Tutor} \hfill 
    Fall 2010 - Present \\
        University of Puget Sound\\
        \begin{itemize}  
            \item Tutored several hours weekly during scheduled office hours.
            \item Prepared students for exams with practice problem assistance
              and general guidance.
            \item Directed students in finding appropriate and useful resources
              for study or assistance outside of tutoring hours.
        \end{itemize}

{\sl Computer Science Grader} \hfill 
    Fall 2010 - Spring 2011 \\
        University of Puget Sound\\
        \begin{itemize}  
            \item Graded assignments for an introductory Java course.
            \item Helped professor to critique assignments for future use.
        \end{itemize}
 
{\sl Research Assistant} \hfill        
    Summer 2011 - Present \\
        University of Puget Sound\\
        \begin{itemize}
        \item Develop software for professors to visualize live student 
          behavior in a classroom programming session.
        \item Collaborate with professors to understand their needs and 
          requirements for the product.
        \end{itemize}
  
\vspace*{.1cm}


\section{RELEVANT ACTIVITIES AND\\ COURSES}
{\sl Mathematical Contest in Modelling} \hfill Spring 2011
 		\begin{itemize}
 		\item Collaborated with a team to develop a software simulation
                  of radio repeater coordination.
 		\item Attained the Meritorious designation (top 18\%).
 		\end{itemize}

{\sl Applicable Courses at the University of Puget Sound} \hfill
\begin{itemize}
        \item Math 181 and 280 (Calculus Sequence): Fall 2009-Spring 2010
        \item Math 433 (Abstract Algebra), 471 (Math Modeling), 260 
          (Intermediate Statistics): Fall 2010-Present
\end{itemize}	
\vspace*{.1cm}
 	
\section{ACADEMIC HONORS}
	Phi Eta Sigma Honors Society\\
	Selected into Coolidge Otis Chapman Honors Scholar Program
	

\end{resume}

% HERE I CAN ADD ANY OTHER RELEVANT SECTIONS:
% COMPUTER SKILLS, SPECIFIC EXPERIENCE, ETC.



% CUTOUTS

%{\sl Phi Eta Sigma Honors Society} \hfill Spring 2010 - Present\\           
% 	\begin{itemize}
%		\item Assisted in organizing various fund-raisers.
%		\item Participated in more than 20 hours of community service per semester.
%		\end{itemize}

\end{document}







