\message{ !name(resume.tex)}% LaTeX resume using res.cls
\documentclass[line,margin,11pt]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\addtolength{\oddsidemargin}{-.5in}
	\addtolength{\evensidemargin}{-.5in}
	\addtolength{\textwidth}{.6in}

	\addtolength{\topmargin}{-.5in}
	\addtolength{\textheight}{1.75in}
\begin{document}

\message{ !name(resume.tex) !offset(-3) }


\name{Kyle Wenholz}
% \address used twice to have two lines of address
\address{1311 N. Alder, Tacoma, WA 98406}
\address{(406) 546-9210, kwenholz@pugetsound.edu}

 
\begin{resume}
\vspace*{.55cm}
\section{OBJECTIVE} AN INTERNSHIP
 
\section{EDUCATION} {\sl Bachelor of Science} \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                University of Puget Sound, Tacoma, WA 
                expected June 2013 \\
                Majors: Mathematics, Computer Science \\
                Cumulative GPA: 3.77

\vspace*{.5cm}

 
\section{EXPERIENCE} 

{\sl Student Researcher} \hfill            
Summer 2011 \\
University of Puget Sound\\
Mathematics and Computer Science Department,
Tacoma, WA
\begin{itemize}  
    \item Developed a plugin for the BlueJ IDE to record 
      programmer behavior (in Java).
    \item Conducted experiments exploring debugging behavior.
\end{itemize} 

{\sl Research Assistant} \hfill
August 2011 - December 2011 \\
University of Puget Sound\\
Mathematics and Computer Science Department,
Tacoma, WA
\begin{itemize}
    \item Prototype software for tracking student behavior.
    \item Construct and maintain a server for database collection of 
      information and visualization component.
    \item Design an interface for real-time data visualization.
\end{itemize}
                   
\
{\sl Computer Science Tutor and Grader} \hfill 
Fall 2010 - Present \\
University of Puget Sound\\
Mathematics and Computer Science Department,
Tacoma, WA
\begin{itemize}  
    \item Graded assignments for an introductory Java course.
    \item Tutored several hours weekly to assist with various 
      computer
      science courses.
\end{itemize}


\vspace*{.5cm}

 
\section{COMPUTER \\ SKILLS}
   \begin{tabular}{l p{3in}}
   \underline{Languages:} & Java, Python, JavaScript, HTML \\
   \underline{Software:} &  Sage Mathematics, Eclipse, Emacs\\
   \underline{Miscellaneous:} & Proficient with LaTex and\\
    & familiar with Git and Mercurial source control systems
   				\end{tabular}  
\vspace*{.5cm}

 
\section{Additional Experience}
{\sl Mathematical Contest in Modelling} \hfill Spring 2011
 		\begin{itemize}
 		\item Collaborated with a team to develop a software 
                  simulation of radio repeater coordination.
 		\item Attained the Meritorious designation (top 18\%).
 		\end{itemize}
 	
\vspace*{.5cm}
 	
 	
\section{ACADEMIC HONORS}
	Phi Eta Sigma Honors Society\\
	Selected into Coolidge Otis Chapman Honors Scholar Program
	

\end{resume}

% HERE I CAN ADD ANY OTHER RELEVANT SECTIONS:
% COMPUTER SKILLS, SPECIFIC EXPERIENCE, ETC.



% CUTOUTS

%{\sl Phi Eta Sigma Honors Society} \hfill Spring 2010 - Present\\           
% 	\begin{itemize}
%		\item Assisted in organizing various fund-raisers.
%		\item Participated in more than 20 hours of community service per semester.
%		\end{itemize}

\end{document}








\message{ !name(resume.tex) !offset(-130) }
