% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\DeclareOption{11pt}{\PassOptionsToClass{11pt}{article}}

\DeclareOption{12pt}{\PassOptionsToClass{12pt}{article}}

%\PassOptionsToClass{11pt,12pt}{article}

\addtolength{\oddsidemargin}{-.5in}
	\addtolength{\evensidemargin}{-.5in}
	\addtolength{\textwidth}{.6in}

	\addtolength{\topmargin}{-.5in}
	\addtolength{\textheight}{1.9in}

% A custom itemize environment
\newenvironment{itemize*}%
  {\begin{itemize}%
    \setlength{\parsep}{0pt}
    \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
  {\end{itemize}}

\begin{document}

\name{\LARGE{Kyle Wenholz}}
% \address used twice to have two lines of address
\address{2214 N. Washington Street, Tacoma, WA 98406} 
\address{kwenholz@pugetsound.edu\hspace*{2mm} \vline \hspace*{2mm} (406)546-9210}

 
\begin{resume}
\vspace*{.3cm}

\section{EDUCATION} {\sl University of Puget Sound, Tacoma, WA} \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Bachelor of Science
                expected May 2013 \\
                Cumulative GPA: 3.77\\
                \textbf{Majors}: \\
\hspace*{5mm}                Mathematics, Computer Science \\
                \textbf{Honors}:\\
\hspace*{5mm}   Selected into Coolidge Otis Chapman Honors Scholar Program\\
\hspace*{5mm}   Upsilon Pi Epsilon Member\\

\vspace*{.2cm}

\section{EXPERIENCE} 

\textbf{CentsLess LLC}, Tacoma, WA
{\sl Lead Engineer} \hfill May 2012 - Present
\begin{itemize*}
    \item Implement back and front-end development of a web application
        to enable peer to peer sharing.
    \item Architect and maintain databases, web servers, and testing framework.
    \item Administrate development related accounts, services, and technology
        choices.
\end{itemize*}

\textbf{Intel Corporation}, Dupont, WA

{\sl Intern BIOS Engineer} \hfill May 2012 - August 2012
\begin{itemize*}
    \item Validated mission-critical server BIOS as part of a large team.
    \item Interpreted and implemented Klocwork security scans, enhancing 
        code reliability and minimizing vulnerabilities.
    \item Assembled data visualizations with Tableau for team metrics and 
        presentations.
\end{itemize*}            

\textbf{Mathematics and Computer Science Department},
University of Puget Sound,\\
Tacoma, WA

{\sl Computer Science Tutor and Grader} \hfill Fall 2010 - Present
\begin{itemize*}  
    \item Grade assignments for an introductory Java course: submitting 
      error logs, testing results, and written reports.
    \item Tutor three to six students several hours weekly.
\end{itemize*}

{\sl Research Assistant} \hfill August 2011 - December 2011
\begin{itemize*}
    \item Prototyped software for tracking student behavior.
    \item Constructed and maintained a server for database collection of 
      information and visualization component.
    \item Designed an instructor interface for real-time, in class, data 
      visualization.
\end{itemize*}            

\vspace*{.2cm}

\section{ACTIVITIES}

\begin{itemize*}
\item Association for Computing Machinery Co-President (May 2012 - Present): gather
    students for regular work on the department website, technical lectures,
    social outings, and educational conventions in the community.
\item Competitor, Mathematical Contest in Modeling: Collaborated on a team of three to 
    develop software simulations of radio repeater coordination (2011, top \%18) and river 
    raft trips (2012, top \%38) presented in a technical paper for the contest.\\
\end{itemize*}

\vspace*{.2cm} 

\section{COMPUTER \\ SKILLS}

\begin{tabular}{l l}
   \underline{Languages:} & Python, Java, HTML, SQL\\
   \underline{Software:} & Django, Vim, Tableau, Eclipse, Sage Mathematics\\
   \underline{Miscellaneous:} & Proficient with LaTeX. \\
                              &  Familiar with Git source control and Linux systems.
  \end{tabular}


\end{resume}

\end{document}







